Placeholder

### 2021-02-13 Paper_Histograms.Rmd
Changed x and y axis text to black on retro diagnosis graph

retro_diagnosis_plot <- dat.retro_positive_diagnosis_by_sample %>% 
  ggplot(aes(x = reorder(Diagnosis, -positive_n, sum), y = positive_n, fill = Sample_plot)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "Mental health diagnosis",
       y = "N participants") +
  ylim(0, 20000) +
  theme(axis.text.x = element_text(angle = 70, vjust = 0.5)) +
  theme(legend.position = "top") + 
  theme(legend.title = element_blank()) +
  geom_text(aes(label = stat(y), group = Diagnosis),
            stat = "summary",
            fun = sum,
            vjust = -1)

>>>>

retro_diagnosis_plot <- dat.retro_positive_diagnosis_by_sample %>% 
  ggplot(aes(x = reorder(Diagnosis, -positive_n, sum), y = positive_n, fill = Sample_plot)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "Mental health diagnosis",
       y = "N participants") +
  ylim(0, 20000) +
  theme(axis.text.x = element_text(angle = 70, vjust = 0.5)) +
  theme(legend.position = "top") + 
  theme(legend.title = element_blank()) +
  geom_text(aes(label = stat(y), group = Diagnosis),
            stat = "summary",
            fun = sum,
            vjust = -1,
            colour = "black") +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))
